\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{longtable}
\usepackage{lscape}

\begin{document}
	\begin{landscape}
		\begin{longtable}{| m{3.5cm} | m{4cm} | m{5cm} | m{6cm} |}
			\hline
			\textbf{Tense} & \textbf{Format} & \textbf{Example} & \textbf{When \& Where to Use It} \\
			\hline
			Past Perfect & had + past participle & She \textbf{had eaten} before she left. & To show an action that happened \textbf{before another past action}. \\
			\hline
			Past Perfect Continuous & had been + verb-ing & She \textbf{had been eating} for 15 minutes. & To emphasize \textbf{duration} before a past event. \\
			\hline
			Simple Past & verb (past form) & She \textbf{ate} at 7 a.m. & For \textbf{completed actions} in the past at a specific time. \\
			\hline
			Past Continuous & was/were + verb-ing & She \textbf{was eating} when I called. & For \textbf{ongoing past actions} interrupted by another action. \\
			\hline
			Present Perfect & has/have + past participle & She \textbf{has eaten} already. & For actions that happened \textbf{at an unspecified time} before now; the result matters now. \\
			\hline
			Present Perfect Continuous & has/have been + verb-ing & She \textbf{has been eating} since 7. & To show how long something has been happening \textbf{up to now}. \\
			\hline
			Simple Present & verb (base) / verb+s & She \textbf{eats} at 7 a.m. & For \textbf{habits, facts, and routines}. \\
			\hline
			Present Continuous & am/is/are + verb-ing & She \textbf{is eating} right now. & For actions \textbf{happening now or around now}. \\
			\hline
			Future Perfect & will have + past participle & She \textbf{will have eaten} by 8 a.m. & To show that an action \textbf{will be completed before} a future point in time. \\
			\hline
			Future Perfect Continuous & will have been + verb-ing & She \textbf{will have been eating} for 30 minutes. & To emphasize \textbf{duration} of an ongoing action up to a future moment. \\
			\hline
			Simple Future & will + verb (base) & She \textbf{will eat} at 7 a.m. & For general \textbf{future events or spontaneous decisions}. \\
			\hline
			Future Continuous & will be + verb-ing & She \textbf{will be eating} at 7:30 a.m. & For \textbf{ongoing actions} at a future specific time. \\
			\hline
		\end{longtable}
	\end{landscape}
	
	
\end{document}
